Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-04-29 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
Comments on text.

  Mathematically modeling complex transport phenomena can be a
  powerful tool for extracting important physical information from 
  molecular simulations. In this study, we present two new approaches 
  that use stochastic time series modeling to predict long-time scale 
  behavior and macroscopic properties from molecular simulation which
  can be generalized to other molecular systems where complex diffusion
  occurs.
  %BJCA: eliminated repetition and merged paragraphs, since the following is one sentence
  %In this study, we use two different stochastic time series modeling approaches parameterized 
  Specifically, we parameterize our models using long molecular dynamics (MD) simulation
  trajectories of a cross-linked H\textsubscript{II} phase lyotropic liquid
  crystal (LLC) membrane in order to predict solute mean squared displacements (MSDs)
  and solute flux, and thus solute selectivity, in macroscopic length pores.

@@

  Next, we present an approach that generalizes Markov state models,
  treating the configurational states of the system as a Markov
  process where each state has distinct transport properties. For each
  state and transition between states, we parameterize the
  distribution and temporal correlation structure of positional
  fluctuations as a means of characterization and to allow us to
  predict solute MSDs. 
  %BJCA: should we add a pargraph break here? Kind of short, but doesn't quite fit with above
  We show that both models reasonably reproduce
  the MSDs calculated from MD simulations. However, qualitative
  differences between MD and Markov state dependent model-generated
  trajectories may limit its usefulness.

  Finally, we demonstrate how one can use these models to estimate
  flux of a solute across a macroscopic-length pore and, based on
  those quantities, the membrane's selectivity towards each
  solute. This work therefore helps to connect microscopic,
  chemically-dependent solute motions that do not follow simple
  diffusive behavior with long-time scale behavior, in an approach
  %BJCA: should hyphen in long-time scale be there? I would favor the pronunciation that goes with long time-scale with or w/o the hyphen
  generalizable to many kinds of molecular systems with complex dynamics.

@@

  % BJCA: Would it make more sense to have the first paragraph less
  % applications-focused and more centered around a need for our new methods?
  % Something like .. 
  There is a large disparity between the time scales accessible to atomistic
  molecular dynamics (MD) simulations and experiment.
  \begin{itemize}
    \item The dynamics of molecules over nanoseconds of simulation may
    tell a very different story than that inferred by bulk measurements
    on the time scale of seconds.
    %BJCA: can cite something about different diffusive regimes 
    \item Understanding complex dynamical behavior on short timescales 
    and connecting them with much longer timescales can provide 
    fundamental insight which can be used for atomic level design of
    materials.
    \item In this work, we pursue this connection applied to highly 
    selective aqueous filtration membranes and demonstrate how one can
    gain chemical intuition which serves both theoretical and 
    experimental researchers.
  \end{itemize}

@@

  % BJCA: I could likely condense this paragraph to focus primarily on the HII phase
  % and its complex pores.
  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
  can be cross-linked into mechanically strong and highly selective nanoporous
  membranes.~\cite{gin_polymerized_2008} They may provide a promising
  alternative to conventional membrane separation techniques by being selective
  based not only on solute size and charge, but on solute chemical
  functionality as well.~\cite{dischinger_application_2017} One can tune the
  functionality of LLC monomers in order to enhance or weaken specific
  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
  morphologies of LLC membranes are being actively developed. The inverted
  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
  pores on the order of 1 nm in size. A perfectly synthesized
  H\textsubscript{II} phase has an ideal geometry for high throughput
  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
  a large scale as required for high permeability has shown limited
  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
  complex pores of the H\textsubscript{II} phase but its geometry consists of a
  tortuous network of 3D interconnected pores which do not require
  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to produce 
  at scale.~\cite{hatakeyama_nanoporous_2010}

@@

  %BJCA: maybe this paragraph can be cut down?
  Mathematical descriptions of transport in complex separations membranes are a
  powerful way to understand mechanisms and formulate design principles.
  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
  In dense homogeneous membranes, the solution-diffusion model
  can extract diffusion and partition coefficients and has successfully
  predicted solute transport rates.~\cite{wijmans_solution-diffusion_1995}
  Analogously, pore-flow models yield predictions of diffusion coefficients and
  solute transport rates in nanoporous membranes.~\cite{paul_diffusive_1974}
  Modern single particle tracking approaches have taken researchers beyond
  continuum modeling allowing them to characterize complex diffusive
  behavior.~\cite{manzo_review_2015} At the molecular level, one can use
  molecular dynamics (MD) simulations to study both single particle dynamics
  and bulk transport properties with atomic-level
  insight.~\cite{coscia_chemically_2019,maginn_best_2018} All of these
  approaches facilitate generation of hypotheses about the molecular origins of
  separations by attempting to give a more intuitive understanding of how
  solutes move as a function of their environment, in turn suggesting
  experiments that could be performed.

@@

  In this work, we use the output of our MD simulations to construct two
  classes of mathematical models which aim to predict membrane performance
  while providing quantitative mechanistic insights. The functional forms of
  these models are driven by mechanistic observations from our previous work and
  their inputs are parameterized using a substantial amount of data generated
  by long ($\geq 5~\mu$s) MD simulations.

  % BJCA: resurrected this paragraph
  We constructed our first model by applying the existing rigorous theoretical
  foundation which describes the motion of particles that exhibit non-Brownian,
  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
  introduced by fractional calculus are instrumental to this
  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
  normally linear diffusion equation to fractional derivative orders, providing
  descriptions of a much more diverse set of behavior, including subdiffusion,
  a type of anomalous diffusion exhibited by solutes in this on the simulation 
  time scales of this study.~\cite{klages_anomalous_2008}
  % BJCA: removing less technical version of above
%  The first model that we develop in this work allows us to characterize the 
%  hopping and trapping behavior displayed by solutes in our MD simulations. This 
%  type of non-Brownian dynamical behavior results in subdiffusive transport which
%  is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}
  %MRS12: removing paragraph break
  We treat our system in terms of two well-known classes of anomalous
  subdiffusion: fractional Brownian motion (FBM) subordinate to a 
  continuous time random walk (CTRW), or subordinated FBM (sFBM) for short. 
  FBM is common in crowded, viscoelastic environments where each jump comes 
  from a Gaussian distribution but is anti-correlated to its previous steps.
  ~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  A pure CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories consist of sequential independent random draws from each
  distribution.~\cite{montroll_random_1965} If the draws are not independent,
  then the hop sequence generation process can be described as subordinate to
  the CTRW. In our case, we observe anti-correlated draws from the hop distribution
  suggesting an FBM process is subordinate to the CTRW.

%BJCA: I could replace above with this, but I think I like the above better. It's more concise.
%  Three well-known classes of behavior leading to anomalous subdiffusion are
%  continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
%  random walks on fractals (RWFs).\cite{meroz_toolbox_2015} These types of
%  motion are frequently used alone or in combination to describe single
%  particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014} A CTRW
%  is characterized by a distribution of hop lengths and dwell times, where
%  trajectories consist of sequential independent random draws from each
%  distribution.\cite{montroll_random_1965} FBM is common in crowded,
%  viscoelastic environments where each jump comes from a Gaussian distribution
%  but is anti-correlated to its previous
%  steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
%  An RWF is imposed by a system's geometry. Systems with tortuous pathways and
%  dead ends cause anti-correlated
%  motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}

@@

  % BJCA: Is this paragraph needed? 
  Where sufficiently close to observed data, these fitted sFBM models
  provide a way to propagate information about solute trajectories gathered 
  at the microsecond time scale to realistic experimental time scales. 
  They can also confirm the importance of assumed solute-membrane interactions 
  used to define the model's functional form, and
  suggest missing components. They can help researchers formulate hypotheses to
  explain why a certain set of parameters is characteristic to a specific
  solute.

@@

  % BJCA: Could move most of the following discussion to the SI and just present the time-averaged MSD.
  In this study, we primarily use the MSD as a tool for characterizing the average
  dynamic behavior of solute trajectories. Rather than using them to calculate 
  diffusion constants or to relate our simulations to experimental measurements, we
  compare MSDs calculated from MD simulations to those generated from our models 
  in order to validate those models. Therefore, it is only important that we use a
  consistent definition for calculating the MSD between modeled trajectories and
  directly observed MD trajectories.

@@

  %BJCA: I could get rid of this table and define them in text. 
  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{ccc}
            \hline
	  \hline
	  Dwell Distribution                & ~~~~~~~~~Hop Length Distribution~~~~~~~~~~~ & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
          \hline
	  \end{tabular}
	  \caption{We tested four anomalous diffusion models with various modifications 
	  to the dwell and hop length distributions. We incorporate hop correlation 
	  into all models.}\label{table:anomalous_models}

@@

  %BJCA: maybe this to supporting?
  \begin{figure}
  \centering
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{Using urea as an example, (a) the distribution of hop lengths can be
	  fit by a Gaussian in addition to a more general L\'evy stable
	  distribution, though the L\'evy stable distribution does a better job of
	  capturing the heavier tails and increased density near 0. We explore
	  models fit to both distributions, as Gaussian hops are more convenient
	  to model. (b) The distribution of dwell times is fit well by a power
	  law but it over-estimates the probability density at long dwell
	  times. A power law truncated with an exponential cut-off better
	  describes the probability of long dwell times in our simulations. (c)
	  The hops are negatively correlated to their previous hop. In
	  combination, (a) -- (c) support modeling solutes as either
	  subordinated fractional Brownian or L\'evy motion. All other solutes
	  show similar distributions and autocorrelation functions (see
	  Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
  }\label{fig:anticorrelated_hops}
  \end{figure}

@@

  %BJCA: This section to supporting
  \subsubsection{Stationarity of solute trajectories}\label{section:stationarity}

@@

  % BJCA: could move 2 mode to SI
  \subsubsection{Model predictions}\label{section:AD_all_data}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_hops.pdf}
  \caption{}\label{fig:1mode_AD_hops}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
  \caption{}\label{fig:1mode_AD_dwells}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{hurst_barchart.pdf}
  \caption{}\label{fig:hurst_barchart}
  \end{subfigure}
  \caption{The parameters of the one mode model reveal differences in dynamics
	  between solutes. (a) We parameterized Gaussian,
	  $\mathcal{N}(\sigma)$, and L\'evy stable, $L(\sigma, \alpha_h)$,
	  distributions to describe solute hop lengths. We assume the mean
	  ($\mu$) to be zero for these distributions and no
	  skewness ($\beta = 0$) in the L\'evy stable distributions. High
	  values of $\sigma$ and lower values of $\alpha_h$ result in larger
	  hops. (b) We parameterized a pure power law, $P(\alpha)$, and a
	  truncated power law, $P_T(\alpha, \lambda)$, distribution to describe
	  solute dwell times. Lower values of $\alpha$ lead to heavier power
	  law tails and higher values of $\lambda$ truncate the distribution at
	  lower dwell times. (c) Finally, we parameterized the hop
	  autocorrelation function, $\gamma(H)$, to describe the degree of
	  correlation between hops. Simulations with higher values of $H$ display
	  behavior closer to the Brownian limit.}\label{fig:1mode_parameters}
  \end{figure}

@@

@@

  %BJCA: potentially move this to SI
  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison.pdf}
  \caption{}\label{fig:gaussian_levy_comparison}
  \end{subfigure}
  % /figures/msddm_acf.py
  \begin{subfigure}{0.42\textwidth}
  \includegraphics[width=\textwidth]{msddm_acf.pdf}
  \caption{}\label{fig:msddm_acf}
  \end{subfigure}
  \caption{(a) The emission distributions of hop lengths are non-Gaussian and
	  heavy-tailed. Shown here is the emission distribution for transitions
	  between states. The maximum likelihood Gaussian fit severely
	  underestimates the empirical density of hops near and far from zero
	  while overestimating the density of hops at intermediate values. (b)
	  Jumps drawn from the transition distribution are negatively
	  correlated to each other. The normalized version of
	  Equation~\ref{eqn:flm_autocovariance} fits well to the data
	  suggesting FLM is an appropriate way to model jumps.}
	  \label{fig:msddm_emissions}
  \end{figure}

@@

  % BJCA: Perhaps replace above paragraph with the following:? 
  In a broader context, it is clear that time series modeling may be a useful way
  to form a lucid connection between complex solute dynamics on the nanosecond 
  timescale and macroscopic observables.
  \begin{itemize}
    \item On the nanoscopic scale, one can both learn and characterize dynamical
    modes in order to identify areas of potentially impactful molecular-level design
    changes. 
    \item For example, it may be possible to modify solute transport rates and 
    selectivities in LLC membranes by redesigning the LLC monomers to mitigate or 
    enhance their chemically dependent interactions with different solutes.
    \item With these models, dynamics can be propagated onto much longer time 
    with computational ease.
    \item This allows one not only to predict a macroscopic observable for a specific
    system, but to explicitly calculate the effect of perturbations to model parameters
    that may result from a monomer design change.
    \item Overall, we hope that this work can advance the reader's understanding of
    how one can apply time series analysis in order to understand complex diffusive 
    behavior in any system of interest.
  \end{itemize}

@@

  We thank Richard Noble for helping us make the connection between the empirical 
  mean first passage time distribution and the analytical equation to which we fit
  the distributions (Equation~\ref{eqn:passage_times}).

  This work was supported in part by the ACS Petroleum Research Fund grant
  \#59814-ND7 and the Graduate Assistance in Areas of National Need (GAANN)
  fellowship which is funded by the U.S. Department of Education.  Molecular
  simulations were performed using the Extreme Science and Engineering
  Discovery Environment (XSEDE), which is supported by National Science
  Foundation grant number ACI-1548562. Specifically, it used the Bridges
  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
  Supercomputing Center (PSC). This work also utilized the RMACC Summit
  supercomputer, which is supported by the National Science Foundation (awards
  ACI-1532235 and ACI-1532236), the University of Colorado Boulder, and
  Colorado State University. The Summit supercomputer is a joint effort of the
  University of Colorado Boulder and Colorado State University.

>>>>

  Mathematically modeling complex transport phenomena can be a
  powerful tool for extracting important physical information from 
  molecular simulations. In this study, we present two new approaches 
  that use stochastic time series modeling to predict long time-scale 
  behavior and macroscopic properties from molecular simulation which
  can be generalized to other molecular systems where complex diffusion
  occurs.
  Specifically, we parameterize our models using long molecular dynamics (MD) simulation
  trajectories of a cross-linked H\textsubscript{II} phase lyotropic liquid
  crystal (LLC) membrane in order to predict solute mean squared displacements (MSDs)
  and solute flux, and thus solute selectivity, in macroscopic length pores.

@@

  Next, we present an approach that generalizes Markov state models,
  treating the configurational states of the system as a Markov
  process where each state has distinct transport properties. For each
  state and transition between states, we parameterize the
  distribution and temporal correlation structure of positional
  fluctuations as a means of characterization and to allow us to
  predict solute MSDs.

  %MRS: combined the ``general'' material about models here.  
  We show that both stochastic models reasonably reproduce the MSDs
  calculated from MD simulations. However, qualitative differences
  between MD and Markov state dependent model-generated trajectories
  may in some cases limit their usefulness. With these parameterized
  stochastic models, we demonstrate how one can estimate flux of a
  solute across a macroscopic-length pore and, based on those
  quantities, the membrane's selectivity towards each solute. This
  work therefore helps to connect microscopic, chemically-dependent
  solute motions that do not follow simple diffusive behavior with
  long time-scale behavior, in an approach generalizable to many types
  of molecular systems with complex dynamics.

@@

  %MRS: agreed.
  % BJCA: Would it make more sense to have the first paragraph less
  % applications-focused and more centered around a need for our new methods?
  % Something like ..

There is a large disparity between the time scales accessible to
atomistic molecular dynamics (MD) simulations and experiment. The
dynamics of molecules over nanoseconds of simulation may tell a very
different story than that inferred by bulk measurements on the time
scale of seconds. Understanding complex dynamical behavior on short
timescales and connecting them with much longer timescales can provide
fundamental insight which can be used for atomic level design of
materials. In this work, we pursue this connection applied to highly
selective aqueous filtration membranes and demonstrate how one can
gain chemical intuition which serves both theoretical and experimental
researchers.

@@

  % BJCA: I could likely condense this paragraph to focus primarily on the HII phase
  % and its complex pores.
  %MRS: yes.  QI not relevant
  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
  can be cross-linked into mechanically strong and highly selective nanoporous
  membranes.~\cite{gin_polymerized_2008} They may provide a promising
  alternative to conventional membrane separation techniques by being selective
  based not only on solute size and charge, but on solute chemical
  functionality as well.~\cite{dischinger_application_2017} One can tune the
  functionality of LLC monomers in order to enhance or weaken specific
  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
  morphologies of LLC membranes are being actively developed. The inverted
  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
  pores on the order of 1 nm in size. A perfectly synthesized
  H\textsubscript{II} phase has an ideal geometry for high throughput
  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
  a large scale as required for high permeability has shown limited
  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
  complex pores of the H\textsubscript{II} phase but its geometry consists of a
  tortuous network of 3D interconnected pores which do not require
  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to produce 
  at scale.~\cite{hatakeyama_nanoporous_2010}

@@

  %BJCA: maybe this paragraph can be cut down?
  %MRS: provides context, so OK?
  Mathematical descriptions of transport in complex separations membranes are a
  powerful way to understand mechanisms and formulate design principles.
  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
  In dense homogeneous membranes, the solution-diffusion model
  can extract diffusion and partition coefficients and has successfully
  predicted solute transport rates.~\cite{wijmans_solution-diffusion_1995}
  Analogously, pore-flow models yield predictions of diffusion coefficients and
  solute transport rates in nanoporous membranes.~\cite{paul_diffusive_1974}
  Modern single particle tracking approaches have taken researchers beyond
  continuum modeling allowing them to characterize complex diffusive
  behavior.~\cite{manzo_review_2015} At the molecular level, one can use
  molecular dynamics (MD) simulations to study both single particle dynamics
  and bulk transport properties with atomic-level
  insight.~\cite{coscia_chemically_2019,maginn_best_2018} All of these
  approaches facilitate generation of hypotheses about the molecular origins of
  separations by attempting to give a more intuitive understanding of how
  solutes move as a function of their environment, in turn suggesting
  experiments that could be performed.

@@

  In this work, we use the output of our MD simulations to construct two
  classes of mathematical models which aim to predict membrane performance
  while providing quantitative mechanistic insights. The functional forms of
  these models are driven by mechanistic observations from our previous work and
  their inputs are parameterized using a substantial amount of data generated
  by long ($\geq 5~\mu$s) MD simulations. 
  %MRS: moved from below
  Where sufficiently close to observed data, these fitted models
  provide a way to propagate information about solute trajectories gathered 
  at the microsecond time scale to realistic experimental time scales.

  % BJCA: resurrected this paragraph
  % MRS: seems OK.
  We constructed our first model by applying the existing rigorous theoretical
  foundation which describes the motion of particles that exhibit non-Brownian,
  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
  introduced by fractional calculus are instrumental to this
  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
  normally linear diffusion equation to fractional derivative orders, providing
  descriptions of a much more diverse set of behavior, including subdiffusion,
  a type of anomalous diffusion exhibited by solutes in this on the simulation 
  time scales of this study.~\cite{klages_anomalous_2008}
  % BJCA: removing less technical version of above
%  The first model that we develop in this work allows us to characterize the 
%  hopping and trapping behavior displayed by solutes in our MD simulations. This 
%  type of non-Brownian dynamical behavior results in subdiffusive transport which
%  is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}
  %MRS12: removing paragraph break
  We treat our system in terms of two well-known classes of anomalous
  subdiffusion: fractional Brownian motion (FBM) subordinate to a 
  continuous time random walk (CTRW), or subordinated FBM (sFBM) for short. 
  FBM is common in crowded, viscoelastic environments where each jump comes 
  from a Gaussian distribution but is anti-correlated to its previous steps.
  ~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  A pure CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories consist of sequential independent random draws from each
  distribution.~\cite{montroll_random_1965} If the draws are not independent,
  then the hop sequence generation process can be described as subordinate to
  the CTRW. In our case, we observe anti-correlated draws from the hop distribution
  suggesting an FBM process is subordinate to the CTRW.

%MRS: more concise better.
%BJCA: I could replace above with this, but I think I like the above better. It's more concise.
%  Three well-known classes of behavior leading to anomalous subdiffusion are
%  continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
%  random walks on fractals (RWFs).\cite{meroz_toolbox_2015} These types of
%  motion are frequently used alone or in combination to describe single
%  particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014} A CTRW
%  is characterized by a distribution of hop lengths and dwell times, where
%  trajectories consist of sequential independent random draws from each
%  distribution.\cite{montroll_random_1965} FBM is common in crowded,
%  viscoelastic environments where each jump comes from a Gaussian distribution
%  but is anti-correlated to its previous
%  steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
%  An RWF is imposed by a system's geometry. Systems with tortuous pathways and
%  dead ends cause anti-correlated
%  motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}

@@

  % BJCA: Is this paragraph needed? 
  %MRS: the first sentence is key to the paper thesis and deserves to be emphasized, but I moved it up.
  %MRS: rest is somewhat redundant.
  %They can also confirm the importance of assumed solute-membrane interactions 
  %used to define the model's functional form, and
  %suggest missing components. They can help researchers formulate hypotheses to
  %explain why a certain set of parameters is characteristic to a specific
  %solute.

@@

  % BJCA: Could move most of the following discussion to the SI and just present the time-averaged MSD.
  %MRS: good call.
  In this study, we primarily use the MSD as a tool for characterizing the average
  dynamic behavior of solute trajectories. Rather than using them to calculate 
  diffusion constants or to relate our simulations to experimental measurements, we
  compare MSDs calculated from MD simulations to those generated from our models 
  in order to validate those models. Therefore, it is only important that we use a
  consistent definition for calculating the MSD between modeled trajectories and
  directly observed MD trajectories.

@@

  %BJCA: I could get rid of this table and define them in text. 
  %MRS: eh, tables are a clear way to communicated data, so OK. 
  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{ccc}
            \hline
	  \hline
	  Dwell Distribution                & ~~~~~~~~~Hop Length Distribution~~~~~~~~~~~ & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
          \hline
	  \end{tabular}
	  \caption{We tested four anomalous diffusion models with various modifications 
	  to the dwell and hop length distributions. We incorporate hop correlation 
	  into all models.}\label{table:anomalous_models}

@@

  %BJCA: maybe this to supporting?
  %MRS: yeah, I think so. 
  \begin{figure}
  \centering
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{Using urea as an example, (a) the distribution of hop lengths can be
	  fit by a Gaussian in addition to a more general L\'evy stable
	  distribution, though the L\'evy stable distribution does a better job of
	  capturing the heavier tails and increased density near 0. We explore
	  models fit to both distributions, as Gaussian hops are more convenient
	  to model. (b) The distribution of dwell times is fit well by a power
	  law but it over-estimates the probability density at long dwell
	  times. A power law truncated with an exponential cut-off better
	  describes the probability of long dwell times in our simulations. (c)
	  The hops are negatively correlated to their previous hop. In
	  combination, (a) -- (c) support modeling solutes as either
	  subordinated fractional Brownian or L\'evy motion. All other solutes
	  show similar distributions and autocorrelation functions (see
	  Figure~\ref{S-fig:anticorrelated_hops} of the Supporting Information).
  }\label{fig:anticorrelated_hops}
  \end{figure}

@@

  %BJCA: This section to supporting
  \subsubsection{Stationarity of solute trajectories}\label{section:stationarity}
  %MRS: yes, though report the results in main text.

@@

  % BJCA: could move 2 mode to SI
  %MRS: Which parts specifically?  Why rationale of 2 mode to SI?  What parts of the results would be presented in main text?What is the main story? (Two model no good, but we tried it, see SI - but that story doesn't seem consistent with the data, they both seem OK)
  \subsubsection{Model predictions}\label{section:AD_all_data}

@@

  %MRS: some of these discussions might belong in the SI, with just the top line information in the main text.  People don't really care about the details of the individual parameters, just what story that tells.   
  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_hops.pdf}
  \caption{}\label{fig:1mode_AD_hops}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
  \caption{}\label{fig:1mode_AD_dwells}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{hurst_barchart.pdf}
  \caption{}\label{fig:hurst_barchart}
  \end{subfigure}
  \caption{The parameters of the one mode model reveal differences in dynamics
	  between solutes. (a) We parameterized Gaussian,
	  $\mathcal{N}(\sigma)$, and L\'evy stable, $L(\sigma, \alpha_h)$,
	  distributions to describe solute hop lengths. We assume the mean
	  ($\mu$) to be zero for these distributions and no
	  skewness ($\beta = 0$) in the L\'evy stable distributions. High
	  values of $\sigma$ and lower values of $\alpha_h$ result in larger
	  hops. (b) We parameterized a pure power law, $P(\alpha)$, and a
	  truncated power law, $P_T(\alpha, \lambda)$, distribution to describe
	  solute dwell times. Lower values of $\alpha$ lead to heavier power
	  law tails and higher values of $\lambda$ truncate the distribution at
	  lower dwell times. (c) Finally, we parameterized the hop
	  autocorrelation function, $\gamma(H)$, to describe the degree of
	  correlation between hops. Simulations with higher values of $H$ display
	  behavior closer to the Brownian limit.}\label{fig:1mode_parameters}
  \end{figure}

@@

  %MRS: this paragraph below may be the sort of summary of the models that would
  %go in the main text, with the details in the SI.

@@

  %BJCA: potentially move this to SI
  %MRS: seems good.  Again, make sure that the conclusions are referenced in the main text. 
  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison.pdf}
  \caption{}\label{fig:gaussian_levy_comparison}
  \end{subfigure}
  % /figures/msddm_acf.py
  \begin{subfigure}{0.42\textwidth}
  \includegraphics[width=\textwidth]{msddm_acf.pdf}
  \caption{}\label{fig:msddm_acf}
  \end{subfigure}
  \caption{(a) The emission distributions of hop lengths are non-Gaussian and
	  heavy-tailed. Shown here is the emission distribution for transitions
	  between states. The maximum likelihood Gaussian fit severely
	  underestimates the empirical density of hops near and far from zero
	  while overestimating the density of hops at intermediate values. (b)
	  Jumps drawn from the transition distribution are negatively
	  correlated to each other. The normalized version of
	  Equation~\ref{eqn:flm_autocovariance} fits well to the data
	  suggesting FLM is an appropriate way to model jumps.}
	  \label{fig:msddm_emissions}
  \end{figure}

@@

  % BJCA: Perhaps replace above paragraph with the following:? 
  % MRS: agreed!
  In a broader context, it is clear that time series modeling may be a useful way
  to form a clear connection between complex solute dynamics on the nanosecond 
  timescale and macroscopic observables.
  \begin{itemize}
    \item On the nanoscopic scale, one can both learn and characterize dynamical
    modes in order to identify areas of potentially impactful molecular-level design
    changes. 
    \item For example, it may be possible to modify solute transport rates and 
    selectivities in LLC membranes by redesigning the LLC monomers to mitigate or 
    enhance their chemically dependent interactions with different solutes.
    \item With these models, dynamics can be propagated onto much longer time 
    with computational ease.
    \item This allows one not only to predict a macroscopic observable for a specific
    system, but to explicitly calculate the effect of perturbations to model parameters
    that may result from a monomer design change.
    \item Overall, we hope that this work can advance the reader's understanding of
    how one can apply time series analysis in order to understand complex diffusive 
    behavior in any system of interest.
  \end{itemize}

@@

  We thank Richard Noble for helping us make the connection between the empirical 
  mean first passage time distribution and the analytical equation to which we fit
  the distributions (Equation~\ref{eqn:passage_times}).
  This work was supported in part by the ACS Petroleum Research Fund grant
  \#59814-ND7 and the Graduate Assistance in Areas of National Need (GAANN)
  fellowship which is funded by the U.S. Department of Education.  Molecular
  simulations were performed using the Extreme Science and Engineering
  Discovery Environment (XSEDE), which is supported by National Science
  Foundation grant number ACI-1548562. Specifically, it used the Bridges
  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
  Supercomputing Center (PSC). This work also utilized the RMACC Summit
  supercomputer, which is supported by the National Science Foundation (awards
  ACI-1532235 and ACI-1532236), the University of Colorado Boulder, and
  Colorado State University. The Summit supercomputer is a joint effort of the
  University of Colorado Boulder and Colorado State University.
